---
title: "Continuing Professional Development Report"
author: "Rhian Davies"
format:
  html:
    theme:
      - lumen
      - custom.scss
    toc: true
    toc-float: true
    number-sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

import_cpd <- function(path) {
  googlesheets4::gs4_deauth()
  tab_names <- googlesheets4::sheet_names(path)
  purrr::map_dfr(tab_names, function(tab) {
    googlesheets4::read_sheet(path, sheet = tab, col_types = "c") |>
      dplyr::mutate(
         #year = as.integer(tab),
        `Start date` = as.Date(`Start date`),
        `End date`   = as.Date(`End date`),
        `Learning hours` = as.numeric(`Learning hours`)
      )
  })
}

df <- import_cpd(
  path = "https://docs.google.com/spreadsheets/d/1m4m3QkoHXUjCDjqz0qTCO883kqQS24-fDmVVrzsNVpY"
) |>
  dplyr::mutate(year = lubridate::year(`Start date`))
```

# Overall summary

This document contains a record of my Continuous Professional Development activities.
CPD should be a key part of a professional statistician's work ethic. CPD means the development of the "whole person" statistical and non-statistical, technical and personal. CPD evaluation is essentially a self-assessment process.

Each year, I should have at least 60 hours of learning hours, across at least three of the following pre-defined categories.

  * Work based learning
  * Professional activity
  * Formal / educational
  * Self-directed learning
  * Other

```{r annual total}
df |>
  dplyr::group_by(year) |>
  dplyr::summarise(total_hours = sum(`Learning hours`, na.rm = TRUE)) |>
  dplyr::mutate(status = ifelse(total_hours >= 60, "\u2705", "\u274c")) |>
  dplyr::arrange(dplyr::desc(year)) |>
  gt::gt() |>
  gt::cols_label(
    year        = gt::md("**Year**"),
    total_hours = gt::md("**Learning Hours**"),
    status      = ""
  ) |>
  gt::tab_style(
    style     = gt::cell_fill(color = "#FAAB18"),
    locations = gt::cells_column_labels()
  )
```

```{r child-reports, results = "asis"}
years <- sort(unique(df$year), decreasing = TRUE)
md <- lapply(years, function(y) {
  knitr::knit_child("annual-template.qmd", envir = environment(), quiet = TRUE)
})
cat(unlist(md), sep = "\n")
```