---
title: "Continuing Professional Development Report"
author: "Rhian Davies"
output:
   html_document:
     theme: united
     toc: true
     toc_float: true
     number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library("lubridate")
library("gt")
library("emo")
library("levelup")
library("dplyr")

df = import_cpd(path = "cpd-records")
```

# Overall summary

This document contains a record of my Continuous Professional Development activities. I work as a Data Scientist and Statistician at [Jumping Rivers](www.jumpingrivers.com). 

CPD should be a key part of a professional statistician's work ethic. CPD means the development of the "whole person" statistical and non-statistical, technical and personal. CPD evaluation is essentially a self-assessment process.

Each year, I should have at least 60 hours of learning hours, across atleast three of the following pre-defined categories. 

  * Work based learning
  * Professional activity
  * Formal / educational
  * Self-directed learning
  * Other


```{r annual total, echo = FALSE}
df = 
  df %>%
  mutate(year = year(start_date)) %>%
  mutate(learning_hours = as.numeric(learning_hours))

df %>% 
  group_by(year) %>% 
  summarise(total_hours = sum(learning_hours)) %>%
  mutate(emoji = ifelse(total_hours >= 60, emo::ji("check"), emo::ji("x"))) %>% 
  arrange(desc(year)) %>% 
  gt() %>% 
  cols_label(
    year = md("**Year**"),
    total_hours = md("**Learning Hours**"),
    emoji = ""
  )
```

```{r, echo = FALSE, results = "asis"}
years = sort(unique(df$year), decreasing = TRUE)

md = lapply(years, function(y) {
  knitr::knit_child(
    'annual-template.Rmd', envir = environment(), quiet = TRUE
  )
})

cat(unlist(md), sep = '\n')
```

